--- 
title: "R markdown权威指南"
author: "Yihui Xie"
date: "`r Sys.Date()`"
bibliography:
- book.bib
- packages.bib
description: This is a minimal example of using the bookdown package to write a book.
  The output format for this example is bookdown::gitbook.
documentclass: book
link-citations: yes
site: bookdown::bookdown_site
biblio-style: apalike
---

# 前言

# 本书使用软件信息

本书使用的R session信息列在下面:


```{r eval=TRUE}
xfun::session_info(c(
  'blogdown', 'bookdown', 'knitr', 'rmarkdown', 'htmltools',
  'reticulate', 'rticles', 'flexdashboard', 'learnr', 'shiny',
  'revealjs', 'pkgdown', 'tinytex', 'xaringan', 'tufte'
), dependencies = FALSE)
```

包的名字使用黑体(例如:**rmarkdown**).函数后面会跟着括号(比如:`blogdown::serve_site()`)."Rmd"是Rmarkdown文件的扩展名,同时也是R markdown的缩写.

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:


<!--chapter:end:index.Rmd-->

# Introduction {#intro}

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].

<!--chapter:end:01-intro.Rmd-->

# Literature

Here is a review of existing methods.

<!--chapter:end:02-literature.Rmd-->

# Methods

We describe our methods in this chapter.

<!--chapter:end:03-method.Rmd-->

# Applications

Some _significant_ applications are demonstrated in this chapter.

## Example one

## Example two

<!--chapter:end:04-application.Rmd-->

# Final Words

We have finished a nice book.

<!--chapter:end:05-summary.Rmd-->

`r if (knitr::is_html_output()) '
# References {-}
'`

<!--chapter:end:06-references.Rmd-->

